Detecting Hand Direction for Computer Interaction

### 2014-12-10 paper/paper.tex
Some paper changes.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\begin{figure}[t]
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointImage.png}
			\caption{} % Just to get the (a)
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2Image.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointHOGedit.png}
			\caption{}
		\end{subfigure}
		\begin{subfigure}[b]{0.45\linewidth}
			\includegraphics[width=\linewidth]{figures/PointLeft2HOGedit.png}
			\caption{}
		\end{subfigure}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure}

@@

\subsection{Smoothing}
In order to make the system more robust to noise, we both smooth the location and eliminate outliers. Let $x[n]$ be the location at frame $n$ and $u[n]$ be the location output from the k-NN and linear regression combination at frame $n$. Outliers are eliminated if
\begin{equation}
	\sqrt{\sum_{i=n-l}^{n}(u[n]-x[i])^2} \geq \epsilon
\end{equation}
where $l$ and $\epsilon$ are parameters representing the amount of history to remember for computing outliers and the sensitivity to outliers, respectively. We used $l=10$ and $\epsilon=200$. Smoothing is implemented by the formula 
\begin{equation}
	x[n+1] = \left\{
		\begin{array}{l l}
			\lambda x[n] + (1-\lambda)u[n] & \qquad \text{if not an outlier} \\
			x[n] & \qquad \text{otherwise}
		\end{array}
	\right.
\end{equation}
 where $\lambda$ is a smoothing parameter between 0 and 1. We used $\lambda=0.5$ to balance quick responsiveness with robustness to noise.

@@

\subsubsection{Performance of Different Regressions}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{}
	\label{fig:hist}
\end{figure*}

\begin{figure*}
	% Figure on bad images
	\begin{center}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftImage.png}
			\caption{} % Just to get the (a)
			\label{fig:pointLeftImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightImage.png}
			\caption{}
			\label{fig:pointRightImage}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointLeftHOG.png}
			\caption{}
			\label{fig:pointLeftHog}
		\end{subfigure}
		\begin{subfigure}[b]{0.4\textwidth}
			\includegraphics[width=\textwidth]{figures/PointRightHOG.png}
			\caption{}
			\label{fig:pointRightHog}
		\end{subfigure}
	\end{center}
	\caption{Examples of images in which our algorithm does not perform as well. The hand is pointing to different points on the screen in images \ref{fig:pointLeftImage} and \ref{fig:pointRightImage}. However, the HOG outputs in \ref{fig:pointLeftHog} and \ref{fig:pointRightHog} are almost identical. This happens because the HOG algorithm mostly detects the outline of the hand and not the pointing finger which is facing mostly toward the camera. Because the HOG images are so similar, the regression does not train properly, causing the blue cursor in \ref{fig:pointLeftImage} and \ref{fig:pointRightImage} to be in the incorrect location.}
	\label{fig:close}
\end{figure*}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Convolution Neural Nets}}\\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 47.8 \\\hline
	Linear Regression &  114.2 \\\hline	
\end{tabular}

\begin{tabular}{|c|c|}
	\hline
	\multicolumn{2}{|c|}{\textbf{Errors for Histogram of Oriented Gradients}} \\\hline
	\textbf{Regression Type} & \textbf{Average Error (Pixels)} \\\hline
	k-Nearest Neighbors & 32.0\\\hline
	Linear Regression & 79.7 \\\hline
	Combined & 47.0 \\\hline
\end{tabular}

\subsection{Evaluation as a Computer Interaction Device}

@@

\section{Conclusion}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}

@@

\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[height=140px]{figures/cnn.png}
	\end{center}
	\caption{This shows a neural network architechture similar to the one used.  We used the values of the second layer from the right as our features.}
	\label{fig:pointImages}
\end{figure*}

\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[height=140px]{figures/PointImage.png}
		\includegraphics[height=140px]{figures/PointHOG.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:pointImages}
\end{figure*}

@@

\subsection{Smoothing}
In order to make the system more robust to noise, we both smooth the location and eliminate outliers. Let $x[n]$ be the location at frame $n$ and $u[n]$ be the location output from the k-NN and linear regression combination at frame $n$. Outliers are eliminated if
\begin{equation}
	\sqrt{\sum_{i=n-l}^{n}(u[n]-x[i])^2} >= \epsilon
\end{equation}
where $l$ and $\epsilon$ are parameters representing the amount of history to remember for computing outliers and the sensitivity to outliers, respectively. We used $l=10$ and $\epsilon=200$. Smoothing is implemented by the formula 
\begin{equation}
	x[n+1] = \left\{
		\begin{array}{l l}
			\lambda x[n] + (1-\lambda)u[n] & \qquad \text{if not an outlier} \\
			x[n] & \qquad \text{otherwise}
		\end{array}
	\right.
\end{equation}
 where $\lambda$ is a smoothing parameter between 0 and 1. We used $\lambda=0.5$ to balance quick responsiveness with robustness to noise.

@@

\subsubsection{Performance of Different Classifiers}
We evaluated the performance of both convolution neural networks and HOG with k-Nearest Neighbors and Linear Regression. The results from our tests our given in figure \ref{fig:hist}, which is a histogram of the error of the different classifiers. The error is the euclidean distance measured in pixels between the predicted point and the actual point.
\begin{figure*}
	\begin{center}
		%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
		\includegraphics[width=0.9\linewidth]{figures/ClassifierErrorHist.png}
	\end{center}
	\caption{An image (on the left) and our corresponding HOG output (on the right). The location calculated by our algorithm is illustrated by the blue dot on the left image.}
	\label{fig:hist}
\end{figure*}
\subsection{Evaluation as a Computer Interaction Device}

@@

\section{Conclusion}
In this work, we explored detecting hand direction in images for interfacing with a computer.  We experimented with HOG as well as convolutional neural network features and tried several different regression methods.  To evaluate the effectiveness of different methods quantitatively, we tried our methods on a set of test images.  Using HOG features and a k-nearest neighbor regression, we achieved an average error of fjdsklfj pixels on these images.  Testing the system qualitatively, we found that the system was not very robust.
